### 2017-01-17 paper/intro.tex
pass on intro

Several approaches have been proposed in the research literature to
address the regression testing problem, with the focus mainly on test
suite minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  In industry, the focus has been
mainly on distributing the testing workloads.  Evidence of this are
the Google TAP system~\cite{google-tap,google-ci} and Microsoft's
CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
provide distributed infrastructures to efficienctly build massive
amounts of code and run tests.  Building server clusters is also a
popular mechanism to distribute testing workloads.  For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.

At large organizations, the alternative of renting cloud
services\footnote{List of popular cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  This paper reports on a study we
conducted analyzing three orthogonal dimensions of regression testing
in open-source projects.  We argue that this an important problem
given the tremendous popularity of open-source development and
regression testing research.  The dimensions of analysis are as
follows.

@@

%%% Local Variables:
%%% TeX-master: "main"
%%% End:

>>>>

Several approaches have been proposed in the research literature to
address the regression testing problem, with the focus mainly on test
suite minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  In industry, the focus has been
mainly on distributing the testing workloads.  Evidence of this are
the Google TAP system~\cite{google-tap,google-ci} and Microsoft's
CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
provide distributed infrastructures to efficiently build massive
amounts of code and run tests.  Building server clusters is also a
popular mechanism to distribute testing workloads.  For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.

At large organizations, the alternative of renting cloud
services\footnote{List of popular cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  The relatively-recent proliferation of
multi-core machines and testing frameworks with a rich support for
parallelization enabled test suites to increase CPU usage (and execute
faster) while using existing resources available in commodity hardware
(see Section~\ref{sec:modes}).  This paper reports on an empirical
study we conducted to analyze importance of test suite parallelization
to speedup testing of open-source projects.  We argue that this a
relevant problem given the tremendous popularity of open-source
development and regression testing research.  The dimensions of
analysis in this study are as follows.

@@

%%% Local Variables:
%%% TeX-master: "main"
%%% End:
%%  LocalWords:  jenkins
